\documentclass[12pt]{developercv}
\begin{document}
\begin{minipage}[t]{0.65\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Bijan Ebrahimi}}}}} % First name
	
	\vspace{6pt}
	
	{\huge Senior C Developer \& Software Designer}\\ % Career or current job title
	{}
\end{minipage}
\begin{minipage}[t]{0.35\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	{Mashhad, Iran}\\
	%{+98 901 963 4978}\\
	{\href{mailto:bijanebrahimi@riseup.net}{bijanebrahimi@riseup.net}}\\	
	{\href{https://bijanebrahimi.github.io/blog}{https://bijanebrahimi.github.io/blog}}\\
	{\href{https://github.com/bijanebrahimi}{github.com/bijanebrahimi}}\\
	%{{Skype:BijanEbrahimi1986}}
	%\icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

%\cvsect{Who Am I?}

%\begin{minipage}[t]{1\textwidth}
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%I am a senior software developer and technical team leader currently working
%at Zharfpouyan.
%Developing and enhancing the core capabilities of the operating system,
%including kernel network stack,
%Designing and implementing (mostly network-based) software solutions, and managing
%technical teams to achieve the project goals is one of my responsibilities.
%\\
%\\
%I like simple solutions over complex designs and I believe that any solution
%can be the base of another problem at some future. So keeping the design simple and
%keeping the code away from the unnecessary complexity is the key to have a
%maintainable and scalable product. So I like BSD projects more due to it's cleaner
%code and design and I like to be part of anything happening around such great projects.

%\end{minipage}
\hfill % Whitespace between
%\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%	\begin{barchart}{5.5}
%		\baritem{C}{100}
%		\baritem{BSD}{90}
%		\baritem{GNU/Linux}{80}
%		\baritem{Git}{90}
%	\end{barchart}
%\end{minipage}
%
%\begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

\cvsect{Skills}
\begin{entrylist}
\entry
{}
{}
{}
{
        \textbf{Operating System Development:} Extensive experience in OS-level programming, including network stack development, in-kernel debugging, and performance optimization on Unix-like systems.

		\textbf{Unix Systems Expertise:} Proficient in designing and deploying secure, production-grade solutions on Linux, FreeBSD, and OpenBSD platforms with a focus on robustness, reliability, redundancy, and security.
		
		\textbf{C Programming \& Scripting:} High proficiency in C with strong skills in shell scripting and Python, particularly for automation and data analytics.
		
		\textbf{WiFi Technology \& Wireless Networks:} Expert in WiFi technology, especially WiFi-6, with extensive experience in optimizing and debugging wireless networks in dense robotic environments.
		
		\textbf{Team Leadership \& Collaboration:} Skilled in managing small engineering teams, leading code reviews, and fostering collaboration and technical discussions.
		
		\textbf{Project Management \& CI/CD:} Proven ability to manage large-scale projects using Git and CI/CD pipelines while adhering to technical processes.
		
		\textbf{Documentation \& Process Adherence:} Strong commitment to creating and following technical documentation and processes, with a focus on secure software practices.
}

\end{entrylist}

\cvsect{Experiences}
\begin{entrylist}
	\entry
		{Ocado\\Technology}
		{Wireless Engineer}
		{2023 - Present}
		{
  			\begin{itemize}
				\itemsep0em
				\item Contributed significantly to the design and implementation of a brand-new, robust, redundant, and secure robot communication system, optimized for high-density wireless robotic environments.
				\item Extended expertise in Wireless 6-E network technologies, focusing on low-latency communications crucial for robotics.
				\item Played a pivotal role in performing thorough performance analysis and optimization to enhance the efficiency and responsiveness of Wireless 6-E networks, ensuring seamless operations in dynamic and dense environments.
			\end{itemize}
		}
	\entry
		{Zharfpouyan}
		{Senior developer \& Technical Leader}
		{2018 - 2022}
		{
			\begin{itemize}
				\itemsep0em
				\item Implemented fully automated network laboratory framework resulting in 95\&
				more accurate and reproducible results, saving engineering time and costs.
				\item Engineered the entire boot process, including Assembly BIOS bootloader ROM, introducing fully encrypted \& secure
				boot to keep-up with security standards with zero cost of upgrading legacy hardwares and
				200\% faster boot time using assembly BIOS programming.
				\item Standardized the technical and manual documentations using customized written \LaTeX
				templates, producing high quality documents.
				\item Designed and implemented new network and security features to kernel and user-space
				programs improving the performance by over 500\% on the same hardware platforms.
				\item Implemented several routing and network protocols on UNIX like operating systems,
				including RSVP-TE and VRRP daemons.
				\item Introduced internal courses with written new highly technical educational materials including
				secure system and network programming topics, increasing the quality of
				new codes code review discussions.
				\item Maintained a proprietary clone of entire FreeBSD project including over 100+ sub-projects
				for over 6 years, adding
				salable MPLS, L2TPv3, mGRE and many more network technologies.
			\end{itemize}

		%Detailed Achievements:
		%\begin{itemize}
		%\end{itemize}
		}
	\entry
		{GetPancake}
		{Co-Founder}
		{2017 - Present}
		{
			Pancake provides manageable and scalable database services that
			are easy to run, maintain and upgrade.\\

			\begin{itemize}
				\itemsep0em
				\item Engineered, tested and deployed the Pancake core infrastructures.\\
				\item Architected Pancake instant full backup solution, 100\% fault tolerant.\\
				\item Designed and Introduced Pancake "Running instances in the past" feature.\\
				%\\
				%\texttt{System Architecture}\slashsep
				%\texttt{System Developer}\slashsep
				%\texttt{DBAAS}\slashsep
			\end{itemize}
		}
	\entry
		{Zharfpouyan}
		{Senior Developer}
		{2016 - 2018}
		{
		%As a senior developer, I developed and maintained Zharf-Router core project
		%infrastructures like kernel network stack, routing services, system utilities,
		%command line and, etc.
		%\\
		%\\
		%Detailed Achievements:
		\begin{itemize}
			\itemsep0em
			\item Extending kernel \& system network functionalities
			\item Remote debugging dead locks and alalyzing the crashes.
			%\item SVN to git migration, Introducting new CI/CD infrastructures
			\item developing fully automated network testing framework laboratory
			\item Adding code reviews and regular code audit processes to the project
			      main development process.
			\item Defining an acceptable level of technical knowledge and standards for
			      developers and designing educational courses
			\item Mentored 10 Junior C developers, training them to work independently and
			      acquire all adequate skills.
		\end{itemize}
		%\texttt{Senior System Developer}\slashsep
		%\texttt{BSD Kernel Developer}\slashsep
		%\texttt{Unix Network Developer}
		}
	\entry
		{Freelance}
		{Full Stack Developer}
		{2004 - 2016}
		{
			\begin{itemize}
				\itemsep0em
				\item Developed lightweight WSGI web applications using flask and MongoDB (2010-2015).
				\item Coding PHP backends and HTML front-ends for customer way back between (2008-2013).
				\item Created scalable and feature-rich CRM application using Delphi and MS-SQL (2004).
				\item Administrating Linux Based Firewalls and Server and develping networked enabled rescue sessions (2010-2012).
				\item Developing Rapidshare proxy server, reducing bandwidth usage at service provider scales at Goldnet.co (2009).
				\item creating customized CRM applications for small businesses like Internet cafe and video clubs, introucing networked capabilities (2005-2010).
			\end{itemize}
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

%\cvsect{Projects}

%\begin{entrylist}
%	\entry
%	{C}
%	{Portable Geli}
%	{hello}
%	{
%		Geli is a portable cryptography tool compatible to FreeBSD geli.
%		
%		\begin{itemize}
%			\itemsep0em
%			\item Currently AES-XTS encryption algorithm for reads and writes.
%			\item Multiple encrption keys of 128 and 256 sizes.
%			\item Password-Based Key Derivation Function.
%			\item Fully compatible with FreeBSD's implementation
%		\end{itemize}
%	}
	%\entry
	%{2005 - 2008}
	%{Bachelor degree in S.E}
	%{Bahar University of Higher Education}
	%{College dropout at the final term}
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{}
		{Bachelor's Coursework in Software Engineering}
		{2005 - 2008}
		{Completed extensive coursework in Software Engineering at Bahar University of Higher Education, with focus on [mention relevant areas or projects if applicable].}

	\entry
		{}
		{Asociate's Degree in Software Engineering}
		{2002 - 2004}
		{Azad University of Mashhad}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

%\begin{minipage}[t]{1.0\textwidth}
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%
%	\cvsect{Languages}
%
%	\textbf{English} - proficient\\
%	\textbf{Persian} - native\\
%\end{minipage}
%\hfill
%\begin{minipage}[t]{1.0\textwidth}
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%	
%	\cvsect{Hobbies}
%	
%	I love reading modern literatures and science/fiction novels. Podcast listener
%	and a science fan.
%	\\
%\end{minipage}
%\hfill
%\begin{minipage}[t]{1.0\textwidth}
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%	
%	\cvsect{Non profit}
%	
%	An active member of Mashhad LUG (Linux User Group) for over 11 years.
%	GUN/Linux advocate and active member of Mashhad LUG commitee
%	for 10 years and recently Co-founder of Mashhad BSD User Group,
%	advoating BSD operating systems and BSD projects.
%
%\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
