\documentclass[12pt]{developercv}
\begin{document}
\begin{minipage}[t]{0.65\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Bijan}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Ebrah‫imi}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Senior System Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.35\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	{Mashhad, Iran}\\
	{+98 901 963 4978}\\
	{\href{mailto:bijanebrahimi@riseup.net}{bijanebrahimi@riseup.net}}\\	
	{\href{https://bijanebrahimi.github.io/blog}{bijanebrahimi.github.io/blog}}\\
	{\href{https://github.com/bijanebrahimi}{github.com/bijanebrahimi}}\\
	%\icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{1\textwidth} % 40% of the page width for the introduction text
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
I am a senior system developer and kernel developer of BSD based
operating systems currently working at ZharfPouyan as the project
development manager of Router project.
Developing and enhancing the core capabilities of the operating system,
designing and implementing software network-based solutions, and managing
technical teams to advance project goals is part of my main interests and
daily jobs.

\end{minipage}
\hfill % Whitespace between
%\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%	\begin{barchart}{5.5}
%		\baritem{C}{100}
%		\baritem{BSD}{90}
%		\baritem{GNU/Linux}{80}
%		\baritem{Git}{90}
%	\end{barchart}
%\end{minipage}
%
%\begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

\cvsect{Experience}
\begin{entrylist}
	\entry
		{2018 - Present}
		{Project Development Manager}
		{Zharfpouyan Co.}
		{
		As a Project Development Manager at \textsc{ZharfRouter} project,
		I am responsible for designing software architectural solutions,
		leading the development team, managing tasks according
		to project's deadlines.
		\\
		\\
		Detailed Achievements:
		\begin{itemize}
			\item Porting Linux Specific codes to other platforms.
			\item Extending kernel's network Stack, adding new protocols
			      and features like customized MPLS network stack,
			      MPLS-TE tunnels, L2TPv3 tunnels and MPLS L2/L3 VPNs.
			\item Porting Intel NIC drivers to some older version of
			      operating-systems;
			\item Defining an acceptable level of technical knowledge for
			      system developers and designing educational courses.
			\item Designing and re-implementation of a new Router Infrastructures
		\end{itemize}
		\texttt{Team Leader}\slashsep
		\texttt{System Architect}\slashsep
		\texttt{Network Stack Developer}
		}
	\entry
		{2017 - 2018}
		{Co-Founder}
		{GetPancake.com}
		{
		Pancake provides manageable and scalable database services that
		are easy to run, maintain and upgrade. As a co-founder,

		Developed a managed database service based on ZFS on Linux
		providing instant database full backup solution and
		redundancy solutions.
		\\
		\texttt{System Architecture}\slashsep
		\texttt{System Developer}
		}
	\entry
		{2016 - 2018}
		{Senior Developer}
		{Zharfpouyan Co.}
		{\lorem \lorem \lorem\\
		\texttt{Senior System Developer}\slashsep
		\texttt{BSD Kernel Developer}\slashsep
		\texttt{Unix Network Developer}
		}
	\entry
		{2012 - 2016}
		{Freelance Developer}
		{}
		{\lorem \lorem \lorem\\
		\texttt{Python}\slashsep
		\texttt{Flask}\slashsep
		\texttt{HTML}\slashsep
		\texttt{CSS}\slashsep
		\texttt{JS}
		}
	\entry
		{2010 - 2012}
		{Linux System Administrator}
		{Freelancer}
		{\lorem \lorem \lorem\\
		\texttt{VPS Management}\slashsep
		\texttt{Firewall}\slashsep
		\texttt{Web Server}\slashsep
		\texttt{VPN Solution}\slashsep
		\texttt{Automation}
		}
	\entry
		{2009 - 2009}
		{Full Stack Developer}
		{GoldNet co.}
		{\lorem \lorem \lorem\\
		\texttt{PHP}\slashsep
		\texttt{MySQL}\slashsep
		\texttt{HTML}\slashsep
		\texttt{CSS}\slashsep
		\texttt{JS}
		}
	\entry
		{2008 - 2012}
		{Freelance Developer}
		{}
		{\lorem \lorem \lorem\\
		\texttt{PHP}\slashsep
		\texttt{MySQL}\slashsep
		\texttt{HTML}\slashsep
		\texttt{CSS}\slashsep
		\texttt{JS}
		}
	\entry
		{2004 - 2008}
		{Freelance Developer}
		{}
		{\lorem \lorem \lorem\\
		\texttt{Delphi}\slashsep
		\texttt{MSSQL}
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2007 - 2009}
		{Bachelor's Degree}
		{Bahar University of higher education}
		{\lorem\lorem}
	\entry
		{2005 - 2007}
		{?}
		{Azad University of Mashhad}
		{\lorem\lorem\lorem}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - proficient\\
	\textbf{Persian} - native\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love to read modern literatures and science/fiction novels.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	An active member of Mashhad Linux User Group for 11+  years.
	GUN/Linux advocate and active member of Mashhad LUG commitee
	for 10+ years.
	Co-founder of Mashhad BSD User Group.
	
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
